---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# proteoME

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/TomChupan/proteoME/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/TomChupan/proteoME/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This package will serve as a useful tool when working with proteomics data. Its main feature is a shiny app that allows you to:

* import your dataset
* deal with missing values
* normalize data
* aggregate data
* analyze data (both univariate and multivariate analysis)

## Installation

You can install the development version of proteoME like so:

``` r
library(devtools)
install_github("TomChupan/proteoME")
```

## Run the app

You can run the app locally as below:

```{r example,eval=F}
library(proteoME)
proteoME::run_app()
```

